Report

### 2021-07-19 Rmd/report.Rmd

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

@@

## Participants {.tabset .tabpills}

* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group). `r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.

### Summary

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

### Longitudinal

We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

@@

## Stimuli {.tabset .tab-pills}

### Frequency {.tabset .tab-pills}

@@

#### CHILDES {.tabset .tab-pills}

@@

#### SUBTLEX {.tabset .tab-pills}

@@

### Familiarity {.tabset .tab-pills}

@@

# Results {.tabset .tab-pills}

## Stringent criteria  {.tabset .tab-pills}

### Growth curve analysis {.tabset .tab-pills}

@@

##### Random effects

@@

#### Marginal means {.tabset .tab-pills}

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

@@

### Attrition {.tabset .tab-pills}

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

@@

left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

@@

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

#### By lexical frequency {.tabset .tab-pills}

@@

#### By familiarity {.tabset .tab-pills}

@@

#### By animacy {.tabset .tab-pills}

@@

#### By category {.tabset .tab-pills}

@@

### 21 month-old monolinguals {.tabset .tab-pills}

@@

```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, lp)

@@

```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, location)

@@

sample_size <- participants %>% 
	drop_na(vocab_size_l1_center) %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
	count(age_group, vocab_cat, lp)

@@

```{r gaze_time_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocabulary (balanced)
sample_size <- participants %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

@@

## Relaxed criteria  {.tabset .tab-pills}

### Growth curve analysis {.tabset .tab-pills}

@@

```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

@@

#### By familiarity {.tabset .tab-pills}

@@

#### By category {.tabset .tab-pills}

@@

## Vocabulary {.tabset .tab-pills}

### L1 vocabulary

@@

### Total vocabulary

>>>>

participants_stringent <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

participants_relaxed <- participants %>% 
	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

@@

## Participants {.tabset .tabset-pills}

### Stringent criteria {.tabset}

* We collected data from `r length(unique(participants_stringent$participant))` participants `r length(unique(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.
* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_stringent$participant[participants_stringent$valid_participant]))` (`r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
* `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group). `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Oxford" & participants_stringent$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Barcelona" & participants_stringent$valid_participant])` were tested in Barcelona.
* From the longitudinal participants, `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])` were tested at two age groups, and `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])`were tested at three age groups.

```{r participants_summary_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_stringent %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

#### Longitudinal

We collected data from `r sum(duplicated(participants_stringent$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.

```{r participants_cohort_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants_stringent %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

### Relaxed criteria {.tabset}

* We collected data from `r length(unique(participants_relaxed$participant))` participants `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.
* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant]))` (`r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
* `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group). `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Oxford" & participants_relaxed$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Barcelona" & participants_relaxed$valid_participant])` were tested in Barcelona.
* From the longitudinal participants, `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])` were tested at two age groups, and `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])`were tested at three age groups.

```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

#### Longitudinal

We collected data from `r sum(duplicated(participants_relaxed$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.

```{r participants_cohort_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

@@

## Stimuli {.tabset }

### Frequency {.tabset }

@@

#### CHILDES {.tabset }

@@

#### SUBTLEX {.tabset }

@@

### Familiarity {.tabset }

@@

# Results {.tabset .tabset-pills}

## Stringent criteria  {.tabset }

### Growth curve analysis {.tabset }

@@

#### Random effects

@@

#### Marginal means {.tabset }

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

@@

### Attrition {.tabset }

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants_stringent %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

@@

left_join(attrition, select(participants_stringent, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

@@

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

#### By lexical frequency {.tabset }

@@

#### By familiarity {.tabset }

@@

#### By animacy {.tabset }

@@

#### By category {.tabset }

@@

### 21 month-old monolinguals {.tabset }

@@

```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, lp)

@@

```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, location)

@@

sample_size <- participants_stringent %>% 
	drop_na(vocab_size_l1_center) %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants_stringent$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
	count(age_group, vocab_cat, lp)

@@

```{r gaze_time_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocabulary (balanced)
sample_size <- participants_stringent %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

@@

## Relaxed criteria  {.tabset }

### Growth curve analysis {.tabset}

@@

```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

@@

```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

@@

#### By familiarity {.tabset}

@@

#### By category {.tabset}

@@

## Vocabulary {.tabset .tabset-pills}

### Stringent criteria {.tabset}

#### L1 vocabulary

@@

#### Total vocabulary
